\documentclass{Resume_Chinnapareddy_2220570} 
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} 
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Chinnapareddy Krishna Vamsi}
\address{(+91)8341192296 \\ kvamc.ch@gmail.com}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{rSection}{Education}
{\bf National Institute of Technology Karnataka, Surathkal} \hfill {\em Aug 2022 - Jul 2024(Expected)} 
\\ Masters in Computer Science.

{\bf V.R Siddhartha Engineering College} \hfill {\em Aug 2015 - May 2019} 
\\ Bachelors in Information Technology. \hfill {\em Overall CGPA: 8.3/10}
\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Work Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{rSection}{Work Experience}
\begin{rSubsection}{Mphasis, India}{Jul 2019 - Oct 2021}{Software Engineer}{}
 \item Good knowledge of software QA methodologies, automation tools and processes.
 \item Developed test scripts for automating the regression process.
 \item Tested cross platform web apps using postman API.
 \end{rSubsection}
\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{rSection}{Projects}
{\bf Recommendation Engine}
\\A novel fashion evaluation method on the basis of the content based filtering in this
paper. The features are extracted from data set according to the characters’ facial feature
method using WordtoVec algorithm. The experimental results show that most similar products that can be accurately described based on the consumers’ interest and the approach has higher application value for the clothing recommendation system.

{\bf Self-Help Groups System}
\\A self-help group (SHG) is a financial intermediary committee usually
composed of 10–20 local women. Self-help groups are started by -governmental
organizations (GO) that generally have broad anti-poverty agendas. Members also make
small regular savings contributions over a few months until there is enough money in the
group to begin lending. To automate this system here we are developing a mobile Android
application which gives all reports related to SHG groups in Andhra Pradesh.
\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Technical Skills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{rSection}{Technical Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages \ & C, C++, Python, Java,  \\
Technologies & HTML5, CSS, Latex\\
Tools & TexMaker, Sublime, Jira, MySql, Postman \\
\end{tabular}
\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Achievements %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{achSection}{Achievements} 
\item Cracked GATE exam with 98.3 percentile.
\item Secured 2nd prize for developing Wireless Charger among 300 projects on Engineer's day 2k16 organized by V.R Siddhartha Engineering College.
\item Bagged 2nd prize for designing Quadcopter on Engineer's Day 2k17 organized by V.R Siddhartha Engineering College.
\end{achSection}

\end{document}
